---
title: "Homework 1"
author: "maekell98"
date: "9/9/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---



**Challenge 1**

```{r Ulysses chunk}
v <- c("Stately", "plump", "Buck", "Mulligan", "came", "from", "the", "stairhead", "bearing", "a", "bowl", "of", "lather", "on", "which", "a", "mirror", "and", "a", "razor", "lay", "crossed", "NA", "NA")

m <- matrix(data = v, nrow =3, ncol = 8, byrow = FALSE)
m

x <- m[3,]
x

```
#coundn't figure out stringr -- "error message: Error in UseMethod("type") : no applicable method for 'type' applied to an object of class "c('double', 'numeric')""

## comment1- I think that the class is technically character? Also Kenny's worked really well, he assigned a vector to each step and he also didn't put each character in quotes (which is what tripped up my code). I pretty much did the same thing as you, but I first tried to make a matrix for some reason and that REALLY didn't work, haha.


**Challenge 2**

```{r matrix chunk}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
m
x <- m[,c(2,3,6)] 
x
#part 1
x <- m[c(6,8),] 
x
#part 2
x <- m[c(2:6), c(2:9)]
x
#part3
```
## comment2- I did the same thing, I think this works


**Challenge 3** 

```{r array chunk}
a <- array(data = 400:1, dim = c(5, 5, 4, 4))
a
a[1, 1, 1, 2]
#returns 300
a[2, 3, 2, ]
#returns 364 264 164  64
a[1:5, 1:5, 3, 3]
#     [,1] [,2] [,3] [,4] [,5]
#[1,]  150  145  140  135  130
#[2,]  149  144  139  134  129
#[3,]  148  143  138  133  128
#[4,]  147  142  137  132  127
#[5,]  146  141  136  131  126
```
## comment3- I like how you included the outputs in your chunk, it makes it really easy to read and I didn't have to run it to see what it spits out


**Challenge 4** 

```{r phylogeny chunk}
Platyrrhini <- c("Cebidea", "Atelidae", "Pitheciidae")
Catarrhini <- c("Cercopithecidea", "Hylobatidae", "Hominidae")
Anthropoidea <- list(Platyrrhini, Catarrhini)
names(Anthropoidea) <- list("Platyrrhini", "Catarrhini")
Anthropoidea
Tarsioidea <- c("Tarsiidae")
Haplorhini <- list(Anthropoidea, Tarsioidea)
names(Haplorhini) <- list("Anthropoidea", "Tarsioidea")
Haplorhini
Lorisoidea <- c("Lorisidae", "Galagidae")
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae", "Daubentoniidae")
Strepsirhini <- list(Lorisoidea, Lemuroidea)
names(Strepsirhini) <- list("Lorisoidea", "Lemuroidea")
Strepsirhini
Primates <- list(Haplorhini, Strepsirhini)
names(Primates) <- list("Haplorhini", "Strepsirhini")
Primates
```

##comment4- I did the same thing but it gave me syntax problems so I'm glad yours works!!


**Challenge 5**

```{r matrix logical/factor chunk}
m3 <- matrix(data = c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow = 5, ncol = 3, byrow = TRUE)
m3
m3.df <- as.data.frame(t(m3))
as.logical(m3.df$Col2)
as.factor(m3.df$Col3)
str(m3.df) 
```
# I think this worked...
## comment5- it looks like it works to me!



**Challenge 2**

```{r matrix chunk}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
m

x <- m[,c(2,3,6)] 
x
#part 1

x <- m[c(6,8),] 
x
#part 2

x <- m[c(2:6), c(2:9)]
x
#part3

```




**Challenge 3** 

```{r array chunk}
a <- array(data = 400:1, dim = c(5, 5, 4, 4))
a

a[1, 1, 1, 2]
#returns 300

a[2, 3, 2, ]
#returns 364 264 164  64

a[1:5, 1:5, 3, 3]
#     [,1] [,2] [,3] [,4] [,5]
#[1,]  150  145  140  135  130
#[2,]  149  144  139  134  129
#[3,]  148  143  138  133  128
#[4,]  147  142  137  132  127
#[5,]  146  141  136  131  126
```



**Challenge 4** 

```{r phylogeny chunk}
Platyrrhini <- c("Cebidea", "Atelidae", "Pitheciidae")
Catarrhini <- c("Cercopithecidea", "Hylobatidae", "Hominidae")
Anthropoidea <- list(Platyrrhini, Catarrhini)
names(Anthropoidea) <- list("Platyrrhini", "Catarrhini")
Anthropoidea
Tarsioidea <- c("Tarsiidae")
Haplorhini <- list(Anthropoidea, Tarsioidea)
names(Haplorhini) <- list("Anthropoidea", "Tarsioidea")
Haplorhini
Lorisoidea <- c("Lorisidae", "Galagidae")
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae", "Daubentoniidae")
Strepsirhini <- list(Lorisoidea, Lemuroidea)
names(Strepsirhini) <- list("Lorisoidea", "Lemuroidea")
Strepsirhini
Primates <- list(Haplorhini, Strepsirhini)
names(Primates) <- list("Haplorhini", "Strepsirhini")
Primates
```




**Challenge 5**

```{r matrix logical/factor chunk}
m3 <- matrix(data = c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow = 5, ncol = 3, byrow = TRUE)
m3

m3.df <- as.data.frame(t(m3))

as.logical(m3.df$Col2)

as.factor(m3.df$Col3)

str(m3.df) 
```
# I think this worked... not really sure what to look for



